---
title: "Assigment 2"
author: "Rueben Campbells4626341" 
date: "08/06/2021"
output: html_document
---


```{r}
library(tidyverse)
library(scales)
library(skimr)
theme_set(theme_light())
```
```{r}
thanksgiving_meals<-read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-20/thanksgiving_meals.csv")
```
#1. Display the first 10 rows of the dataset using RMarkdown
```{r}
thanksgiving_meals%>%head(10)
```
#Use `fct_reorder` and `parse_number` functions to create a factor variable `family_income`
```{r}
thanksgiving_meals%>%
mutate(family_income = fct_reorder(family_income, parse_number(family_income)))
```
#Generate the general statistics of the dataset using `summary()` and `skim()` function
```{r}
thanksgiving_meals%>%summary()
thanksgiving_meals%>%skim()
```
#What is the number of people who celebrate?
```{r}
thanksgiving_meals%>%count(celebrate,sort = TRUE)
```
#What are categories and stats for each main dish served and the method it is prepared?
```{r}
statistics<-thanksgiving_meals%>%
count(main_dish,main_prep,sort = TRUE)
```
#Create a data viz showing this in the most evident way. Provide your own legend and use themes.
```{r}
statistics%>%ggplot(aes(n,main_dish,fill=main_prep))+geom_col()+theme(legend.position = "top")
```
#How many use cranberry sauce? How many use gravy?
```{r}
thanksgiving_meals%>%count(gravy,sort = TRUE)
thanksgiving_meals%>%count(cranberry,sort = TRUE)
```
# What is the distribution of those who celebrate across income ranges
```{r}
income_celebrate<-thanksgiving_meals%>%
group_by(family_income)%>%
summarise(celebrate = sum(celebrate == "Yes"))%>%ungroup()
```
#Present this information in the most evident way on the data viz.
```{r}
income_celebrate%>%
ggplot(aes(celebrate,family_income))+
geom_point()
```
#What are the most common pies, sides, and desserts?
```{r}
common_food<-thanksgiving_meals%>%
select(id, starts_with("side"),
starts_with("pie"),
starts_with("dessert")) %>%
select(-side15,-pie13,-dessert12)%>%
gather(type, value,-id)%>%
filter(!is.na(value),
!value %in% c("None", "Other (please specify)"))%>%
mutate(type = str_remove(type, "\\d+"))
common_food<-common_food%>%
count(type,value,sort = TRUE)
```
#Present this information on a data viz
```{r}
common_food%>%
ggplot(aes(n,value,fill = type))+
geom_col()
```
#How do the servings differ by income?
```{r}
service<-thanksgiving_meals%>%
select(id, starts_with("side"),
starts_with("pie"),
starts_with("dessert"),
starts_with("main_dish")) %>%
select(-side15,-pie13,-dessert12)%>%
gather(type, food,-id)%>%
filter(!is.na(food),
!food %in% c("None", "Other (please specify)"))%>%
mutate(type = str_remove(type, "\\d+"))
service<-service%>%
inner_join(thanksgiving_meals)%>%
mutate(income = parse_number(family_income))%>%
group_by(food)%>%
summarise(family_income)%>%
arrange(family_income)
service<-service%>%count(food,family_income,sort = TRUE)
```
#Present this information on a data viz
```{r}
service%>%ggplot(aes(family_income,food))+geom_point()
```

